---
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(scales)
library(stringr)
library(pander)
#setwd("~/Documents/MSSP/Tala Berro")
t = read.csv("Trans Health in Cancer Genetic Counseling_12.5.17.csv", header  = TRUE)
t = t[-c(1:2),] # delete first two rows

# Q7: Case 3
# Q9: Case 4
# Q10: Case 5
# Q35: Case 6
# Q14: trans specific training
# Q17: age
# Q19: how many years worked in cancer setting
# Q21: gender identity
# Q3: number of patients seen
# Q4: seen any trans
# Q25: region
# Q24: race

tr = select(t,Q7, Q9, Q10, Q35, Q14, Q16, Q17, Q19, Q21, Q3, Q4, Q25, Q24)
tr = droplevels(tr)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
# Remove blanks
#tr = tr[!apply(tr == "", 1, all),]
tr = tr[!(tr$Q7 == "" | tr$Q9 == "" | tr$Q10 == "" | tr$Q35 == ""),]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Case 3 -- Question 7
Q7 = lapply(strsplit(as.character(tr$Q7),","),function(x)as.integer(x))

Q7_c = c(1,2,5) # correct answers
Q7_p = NULL

for(i in 1:length(tr$Q7)) {
  intersect = intersect(Q7[[i]], Q7_c)
  union = union(Q7[[i]], Q7_c)
  Q7_p[i] = length(intersect) / length(union)
}
#Q7_p
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Case 4 -- Question 9
Q9 = lapply(strsplit(as.character(tr$Q9),","),function(x)as.integer(x))

Q9_c = c(1, 2, 6)
Q9_p = NULL

for(i in 1:length(tr$Q9)) {
  intersect = intersect(Q9[[i]], Q9_c)
  union = union(Q9[[i]], Q9_c)
  Q9_p[i] = length(intersect) / length(union)
}
#Q9_p
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Case 5 -- Question 10
Q10 = lapply(strsplit(as.character(tr$Q10),","),function(x)as.integer(x))

Q10_c = c(1, 2, 3, 4, 6)
Q10_p = NULL

for(i in 1:length(tr$Q10)) {
  intersect = intersect(Q10[[i]], Q10_c)
  union = union(Q10[[i]], Q10_c)
  Q10_p[i] = length(intersect) / length(union)
}
#Q10_p
```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Case 6 -- Question 35 with the answer "1, 2, 4"

Q35 = lapply(strsplit(as.character(tr$Q35),","),function(x)as.integer(x))

Q35_c1 = c(1, 2, 4)
Q35_p1 = NULL

for(i in 1:length(tr$Q35)) {
  intersect = intersect(Q35[[i]], Q35_c1)
  union = union(Q35[[i]], Q35_c1)
  Q35_p1[i] = length(intersect) / length(union)
}
#Q35_p1
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Case 6 -- Question 35 with the answer "1, 2, 4, 5"
Q35_c2 = c(1, 2, 4, 5)
Q35_p2 = NULL

for(i in 1:length(tr$Q35)) {
  intersect = intersect(Q35[[i]], Q35_c2)
  union = union(Q35[[i]], Q35_c2)
  Q35_p2[i] = length(intersect) / length(union)
}
#Q35_p2
```

```{r training_data}
tr = droplevels(tr)
tr$Q16 = factor(tr$Q16, labels=c("Yes", "No", "Not Sure"))
tr$Q21 = ifelse(tr$Q21 == "1", "Man", ifelse(tr$Q21 == "2", "Woman", "Others"))
md = data.frame(Q16 = tr$Q16, Q21 = tr$Q21)
m = data.frame(table(md))
ggplot(m, aes(x = Q16, y = Freq, fill = Q21)) + 
  geom_bar(stat = "identity", position = "fill") + 
  xlab("Pursue Further Education/Training") + ylab("Gender") + 
  scale_y_continuous(labels = percent_format())

total = NULL
for (i in 1:length(Q7_p)) {
  total[i] = mean(Q7_p[i], Q9_p[i], Q10_p[i])
}

ggplot(tr, aes(x = Q16, y = total, fill = Q16)) + 
  geom_boxplot() + 
  ggtitle("Differences in Total Performance") + 
  xlab("Pursue Further Education/Training") + ylab("Total Performance")

ggplot(tr, aes(x = Q16, y = Q7_p, fill = Q16)) + 
  geom_boxplot() + 
  ggtitle("Differences in Performance for Case 3") + 
  xlab("Pursue Further Education/Training") + ylab("Performance for Question 7")

ggplot(tr, aes(x = Q16, y = Q9_p, fill = Q16)) + 
  geom_boxplot() + 
  ggtitle("Differences in Performance for Case 4") + 
  xlab("Pursue Further Education/Training") + ylab("Performance for Question 9")

ggplot(tr, aes(x = Q16, y = Q10_p, fill = Q16)) + 
  geom_boxplot() + 
  ggtitle("Differences in Performance for Case 5") + 
  xlab("Pursue Further Education/Training") + ylab("Performance for Question 10")

ggplot(tr, aes(x = Q16, y = Q35_p1, fill = Q16)) + 
  geom_boxplot() + 
  ggtitle("Differences in Performance for Case 6 with the answer '1, 2, 4'") + 
  xlab("Pursue Further Education/Training") + ylab("Performance for Question 35")

ggplot(tr, aes(x = Q16, y = Q7_p, fill = Q16)) + 
  geom_boxplot() + 
  ggtitle("Differences in Performance for Case 6 with the answer '1, 2, 4, 5'") + 
  xlab("Pursue Further Education/Training") + ylab("Performance for Question 35")
```


```{r, echo=FALSE, warning=FALSE}

c1=mean(Q7_p[-which(lapply(Q7, length)==0)])
c2=mean(Q9_p[-which(lapply(Q9, length)==0)])
c3=mean(Q10_p[-which(lapply(Q10, length)==0)])
c4=mean(Q35_p1[-which(lapply(Q35, length)==0)])
c5=mean(Q35_p2[-which(lapply(Q35, length)==0)])

d1=mean(Q7_p)
d2=mean(Q9_p)
d3=mean(Q10_p)
d4=mean(Q35_p1)
d5=mean(Q35_p2)


n = c("Case 3", "Case 4", "Case 5", "Case 6a", "Case 6b")

df = data.frame(cbind(n, round(c(c1,c2,c3,c4),2), round(c(d1,d2,d3,d4,d5),2)))

names(df) = c("Case", "Avg. JI (excl. blank)", "Avg. JI (incl. blanks)")

pander(df)

```




#### Visualizations for Case Study 3

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tr$Q17 <- as.numeric(tr$Q17) 
tr$Age_Band <- ifelse(tr$Q17 < 25, "<= 24", ifelse(tr$Q17 < 35, "25 - 34", ifelse(tr$Q17 < 45, "35 - 44", ifelse(tr$Q17 < 55, "45 - 54", ifelse(tr$Q17 < 65, "55 - 64", ifelse(tr$Q17 > 64, ">= 65", "Blank")))))) # age bands

Q7df <- data.frame(Q7_p, tr$Q14, tr$Q17, tr$Q19, tr$Q21, tr$Age_Band)
colnames(Q7df)[1:6] <- c("p", "Training", "Age", "Experience", "GI", "Age_Band")
Q7df$Correct <- ifelse(Q7df$p == 1, 3, ifelse(Q7df$p == 2/3, 2, ifelse(Q7df$p == 1/3, 1, 0)))
Q7df$Question <- c(7)

## Response Proportions by Training

ggplot(Q7df, aes(x = factor(Training), y = p, color = factor(Training))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Education or Training related to Transgender Health", y = "Jaccard Index", title = "Q7: Response Proportions by Training") +
  scale_x_discrete(labels = c("Blank","Yes","No")) +
  geom_jitter(shape=1, position=position_jitter(0.2))

## Response Proportions by Age Band

ggplot(Q7df, aes(x = factor(Age_Band), y = p, color = factor(Age_Band))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Age", y = "Jaccard Index", title = "Q7: Response Proportions by Age Band") +
  geom_jitter(shape=1, position=position_jitter(0.2))

## Response Proportions by Experience

ggplot(Q7df, aes(x = factor(Experience), y = p, color = factor(Experience))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Years of Experience", y = "Jaccard Index", title = "Q7: Response Proportions by Experience") +
  scale_x_discrete(labels = c("Blank","1-2","3-5", "6-10", ">10")) +
  geom_jitter(shape=1, position=position_jitter(0.2))

## Response Proportions by Gender Identity
ggplot(Q7df, aes(x = factor(GI), y = p, color = factor(GI))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Gender Identity", y = "Jaccard Index", title = "Q7: Response Proportions by Gender Identity") +
  scale_x_discrete(labels = c("Blank","Man","Woman", "Trans Man", "Trans Woman", "Non-Binary", "Decline to Answer", "Other")) +
  geom_jitter(shape=1, position=position_jitter(0.2))
```


#### Visualizations for Case Study 4

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Q9df <- data.frame(Q9_p, tr$Q14, tr$Q17, tr$Q19, tr$Q21, tr$Age_Band)
colnames(Q9df)[1:6] <- c("p", "Training", "Age", "Experience", "GI", "Age_Band")
Q9df$Correct <- ifelse(Q9df$p == 1, 3, ifelse(Q9df$p == 2/3, 2, ifelse(Q9df$p == 1/3, 1, 0)))
Q9df$Question <- c(9)

## Response Proportions by Training

ggplot(Q9df, aes(x = factor(Training), y = p, color = factor(Training))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Education or Training related to Transgender Health", y = "Jaccard Index", title = "Q9: Response Proportions by Training") +
  scale_x_discrete(labels = c("Blank","Yes","No")) +
  geom_jitter(shape=1, position=position_jitter(0.2))

## Response Proportions by Age Band

ggplot(Q9df, aes(x = factor(Age_Band), y = p, color = factor(Age_Band))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Age", y = "Jaccard Index", title = "Q9: Response Proportions by Age Band") +
  geom_jitter(shape=1, position=position_jitter(0.2))

## Response Proportions by Experience

ggplot(Q9df, aes(x = factor(Experience), y = p, color = factor(Experience))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Years of Experience", y = "Jaccard Index", title = "Q9: Response Proportions by Experience") +
  scale_x_discrete(labels = c("Blank","1-2","3-5", "6-10", ">10")) +
  geom_jitter(shape=1, position=position_jitter(0.2))

## Response Proportions by Gender Identity
ggplot(Q9df, aes(x = factor(GI), y = p, color = factor(GI))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Gender Identity", y = "Jaccard Index", title = "Q9: Response Proportions by Gender Identity") +
  scale_x_discrete(labels = c("Blank","Man","Woman", "Trans Man", "Trans Woman", "Non-Binary", "Decline to Answer", "Other")) +
  geom_jitter(shape=1, position=position_jitter(0.2))

```

#### Case 5 Visualizations

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Q10df <- data.frame(Q10_p, tr$Q14, tr$Q17, tr$Q19, tr$Q21, tr$Age_Band)
colnames(Q10df)[1:6] <- c("p", "Training", "Age", "Experience", "GI", "Age_Band")
Q10df$Correct <- ifelse(Q10df$p == 1, 5, ifelse(Q10df$p == .8, 4, ifelse(Q10df$p == .6, 3, ifelse(Q10df$p == .4, 2, ifelse(Q10df$p == .2, 1, 0)))))
Q10df$Question <- c(10)

## Response Proportions by Training

ggplot(Q10df, aes(x = factor(Training), y = p, color = factor(Training))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Education or Training related to Transgender Health", y = "Jaccard Index", title = "Q10: Response Proportions by Training") +
  scale_x_discrete(labels = c("Blank","Yes","No")) +
  geom_jitter(shape=1, position=position_jitter(0.2))

## Response Proportions by Age Band

ggplot(Q10df, aes(x = factor(Age_Band), y = p, color = factor(Age_Band))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Age", y = "Jaccard Index", title = "Q10: Response Proportions by Age Band") +
  geom_jitter(shape=1, position=position_jitter(0.2))

## Response Proportions by Experience

ggplot(Q10df, aes(x = factor(Experience), y = p, color = factor(Experience))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Years of Experience", y = "Jaccard Index", title = "Q10: Response Proportions by Experience") +
  scale_x_discrete(labels = c("Blank","1-2","3-5", "6-10", ">10")) +
  geom_jitter(shape=1, position=position_jitter(0.2))

## Response Proportions by Gender Identity
ggplot(Q10df, aes(x = factor(GI), y = p, color = factor(GI))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Gender Identity", y = "Jaccard Index", title = "Q10: Response Proportions by Gender Identity") +
  scale_x_discrete(labels = c("Blank","Man","Woman", "Trans Man", "Trans Woman", "Non-Binary", "Decline to Answer", "Other")) +
  geom_jitter(shape=1, position=position_jitter(0.2))
```

#### Case 6 Visualizations (without Q5)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Q35p1df <- data.frame(Q35_p1, tr$Q14, tr$Q17, tr$Q19, tr$Q21, tr$Age_Band)
colnames(Q35p1df)[1:6] <- c("p", "Training", "Age", "Experience", "GI", "Age_Band")
Q35p1df$Correct <- ifelse(Q35p1df$p == 1, 3, ifelse(Q35p1df$p == 2/3, 2, ifelse(Q35p1df$p == 1/3, 1, 0)))
Q35p1df$Question <- c(35.1)

## Response Proportions by Training

ggplot(Q35p1df, aes(x = factor(Training), y = p, color = factor(Training))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Education or Training related to Transgender Health", y = "Jaccard Index", title = "Q35 Scenario 1: Response Proportions by Training") +
  scale_x_discrete(labels = c("Blank","Yes","No")) +
  geom_jitter(shape=1, position=position_jitter(0.2))

## Response Proportions by Age Band

ggplot(Q35p1df, aes(x = factor(Age_Band), y = p, color = factor(Age_Band))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Age", y = "Jaccard Index", title = "Q35 Scenario 1: Response Proportions by Age Band") +
  geom_jitter(shape=1, position=position_jitter(0.2))

## Response Proportions by Experience

ggplot(Q35p1df, aes(x = factor(Experience), y = p, color = factor(Experience))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Years of Experience", y = "Jaccard Index", title = "Q35 Scenario 1: Response Proportions by Experience") +
  scale_x_discrete(labels = c("Blank","1-2","3-5", "6-10", ">10")) +
  geom_jitter(shape=1, position=position_jitter(0.2))

## Response Proportions by Gender Identity
ggplot(Q35p1df, aes(x = factor(GI), y = p, color = factor(GI))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Gender Identity", y = "Jaccard Index", title = "Q35 Scenario 1: Response Proportions by Gender Identity") +
  scale_x_discrete(labels = c("Blank","Man","Woman", "Trans Man", "Trans Woman", "Non-Binary", "Decline to Answer", "Other")) +
  geom_jitter(shape=1, position=position_jitter(0.2))
```

#### Case 6 Visualizations (with Q5)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Q35p2df <- data.frame(Q35_p2, tr$Q14, tr$Q17, tr$Q19, tr$Q21, tr$Age_Band)
colnames(Q35p2df)[1:6] <- c("p", "Training", "Age", "Experience", "GI", "Age_Band")
Q35p2df$Correct <- ifelse(Q35p2df$p == 1, 4, ifelse(Q35p2df$p == .75, 3, ifelse(Q35p2df$p == .5, 2, ifelse(Q35p2df$p == .25, 1, 0))))
Q35p2df$Question <- c(35.2)

## Response Proportions by Training

ggplot(Q35p2df, aes(x = factor(Training), y = p, color = factor(Training))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Education or Training related to Transgender Health", y = "Jaccard Index", title = "Q35 Scenario 2: Response Proportions by Training") +
  scale_x_discrete(labels = c("Blank","Yes","No")) +
  geom_jitter(shape=1, position=position_jitter(0.2))

## Response Proportions by Age Band

ggplot(Q35p2df, aes(x = factor(Age_Band), y = p, color = factor(Age_Band))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Age", y = "Jaccard Index", title = "Q35 Scenario 2: Response Proportions by Age Band") +
  geom_jitter(shape=1, position=position_jitter(0.2))

## Response Proportions by Experience

ggplot(Q35p2df, aes(x = factor(Experience), y = p, color = factor(Experience))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Years of Experience", y = "Jaccard Index", title = "Q35 Scenario 2: Response Proportions by Experience") +
  scale_x_discrete(labels = c("Blank","1-2","3-5", "6-10", ">10")) +
  geom_jitter(shape=1, position=position_jitter(0.2))

## Response Proportions by Gender Identity
ggplot(Q35p2df, aes(x = factor(GI), y = p, color = factor(GI))) + 
  geom_boxplot() +
  theme(legend.position="none") + 
  labs(x = "Gender Identity", y = "Jaccard Index", title = "Q35 Scenario 2: Response Proportions by Gender Identity") +
  scale_x_discrete(labels = c("Blank","Man","Woman", "Trans Man", "Trans Woman", "Non-Binary", "Decline to Answer", "Other")) +
  geom_jitter(shape=1, position=position_jitter(0.2))
```

#### Modelling 

The potential covariates broadly fall into two main categories:  

**Clinician Experience**  
1. Number of patients seen each month (<40, ~40, >40)  
2. Number of years spent working in a cancer setting  
3. Seen any transgender patients?  
4. Any transgender specific education/ training?  

**Clinician Demographics**  
1. Age  
2. Gender identity  
3. Sexual orientation  
4. Race  
5. Region of practice  

#### Case Sutdy 3 Linear Model

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Q7: Case 3
# Q9: Case 4
# Q10: Case 5
# Q35: Case 6
# Q14: trans specific training
# Q17: age
# Q19: how many years worked in cancer setting
# Q21: gender identity




m3 = lm(Q7_p~Q14+factor(Age_Band)+Q19+Q21+Q3+Q4+Q24+Q25,data = tr)
pander(m3)

```

#### Case Sutdy 4 Linear Model

```{r, echo=FALSE, message=FALSE, warning=FALSE}
m4 = lm(Q9_p~Q14+factor(Age_Band)+Q19+Q21+Q3+Q4+Q24+Q25,data = tr)
pander(m4)

```

#### Case Sutdy 5 Linear Model

```{r, echo=FALSE, message=FALSE, warning=FALSE}
m4 = lm(Q10_p~Q14+factor(Age_Band)+Q19+Q21+Q3+Q4+Q24+Q25,data = tr)
pander(m4)

```

#### Case Sutdy 6 Linear Model

```{r, echo=FALSE, message=FALSE, warning=FALSE}
m4 = lm(Q35_p1~Q14+factor(Age_Band)+Q19+Q21+Q3+Q4+Q24+Q25,data = tr)
pander(m4)

```

#### Missing Answers' Distribution

```{r, echo=FALSE, message=FALSE, warning=FALSE}
## Case 3 -- Question 7
Q7_m = NULL
for(i in 1:length(tr$Q7)) {
  Q7_m[[i]] = ifelse(length(setdiff(Q7_c, Q7[[i]])) > 0, setdiff(Q7_c, Q7[[i]]), NA)
}
Q7_m = Q7_m[!is.na(Q7_m)]
Q7_d = data.frame(Q7_m)
ggplot(Q7_d, aes(x = Q7_d$Q7_m)) + 
  geom_histogram(aes(fill = ..count..)) + 
  stat_bin(geom="text", aes(label=ifelse(..count.. > 0, ..count.., "")) , vjust = -0.5) + 
  labs(title = "Distribution of Missing Answers for Case 3", x = "Missing Answer", y = "Frequency") +
  scale_x_continuous(breaks = 1:5, labels = 1:5) +
  theme(legend.position="none")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
## Case 4 -- Question 9
Q9_m = NULL
for(i in 1:length(tr$Q9)) {
  Q9_m[[i]] = ifelse(length(setdiff(Q9_c, Q9[[i]])) > 0, setdiff(Q9_c, Q9[[i]]), NA)
}
Q9_m = Q9_m[!is.na(Q9_m)]
Q9_d = data.frame(Q9_m)
ggplot(Q9_d, aes(x = Q9_d$Q9_m)) + 
  geom_histogram(aes(fill = ..count..)) + 
  stat_bin(geom="text", aes(label=ifelse(..count.. > 0, ..count.., "")) , vjust = -0.5) + 
  labs(title = "Distribution of Missing Answers for Case 4", x = "Missing Answer", y = "Frequency") + 
  scale_x_continuous(breaks = 1:6, labels = 1:6) +
  theme(legend.position="none")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
## Case 5 -- Question 10
Q10_m = NULL
for(i in 1:length(tr$Q10)) {
  Q10_m[[i]] = ifelse(length(setdiff(Q10_c, Q10[[i]])) > 0, setdiff(Q10_c, Q10[[i]]), NA)
}
Q10_m = Q10_m[!is.na(Q10_m)]
Q10_d = data.frame(Q10_m)
ggplot(Q10_d, aes(x = Q10_d$Q10_m)) + 
  geom_histogram(aes(fill = ..count..)) + 
  stat_bin(geom="text", aes(label=ifelse(..count.. > 0, ..count.., "")) , vjust = -0.5) + 
  labs(title = "Distribution of Missing Answers for Case 5", x = "Missing Answer", y = "Frequency") + 
  scale_x_continuous(breaks = 1:6, labels = 1:6) +
  theme(legend.position="none")
```